\tool: Programmable, Efficient, and Scalable Secure Two-Party Computation

### 2017-10-28 OaklandSubmission/security.tex

% and upon receiving output $O_1$, executes $\simu_{\tiny{2pc}}$ on $\chi$ and $O_1$. Let $O_2$ be the outputs (or observations) of $\chi$. First, from Theorem \ref{theorem:correctness}, we have that the observations in $s$ and $\chi$ are the same (i.e. $O_2 = O_1$). Now, from the security of $\prot$, we have that the simulated view output by $\simu_{\tiny{2pc}}$ (with circuit $\chi$ and output $O_2$) is indistinguishable from the real view of the $\prot$ (when executed on circuit $\chi$ and when the output is $O_2$). Combining these two statements, the proof of the theorem follows. 
\aseem{
  Also, we should emaphasize here that the ideal semantics is the
  source semantics from Figure x and the real semantics is the circuit
  semantics from Figure y. For the target language semantics, we
  should emphasize that it does not have access to the secrets, so
  there are no observations there.
}

\nc{OK now?}
  %% \\
  %% \[
  %% \begin{array}{rrcl}
  %%   \ftext{Value} & v &::=& c \mid [\overline{c_{i}}]_{n}\\
  %%   \ftext{Observation} & O &::=& \cdot \mid c; O\\
  %% \end{array}
  %% \]

>>>>

% and upon receiving output $O_1$, executes $\simu_{\tiny{2pc}}$ on $\chi$ and $O_1$. Let $O_2$ be the outputs (or observations) of $\chi$. First, from Theorem \ref{theorem:correctness}, we have that the observations in $s$ and $\chi$ are the same (i.e. $O_2 = O_1$). Now, from the security of $\prot$, we have that the simulated view output by $\simu_{\tiny{2pc}}$ (with circuit $\chi$ and output $O_2$) is indistinguishable from the real view of the $\prot$ (when executed on circuit $\chi$ and when the output is $O_2$). Combining these two statements, the proof of the theorem follows. 
  %% \\
  %% \[
  %% \begin{array}{rrcl}
  %%   \ftext{Value} & v &::=& c \mid [\overline{c_{i}}]_{n}\\
  %%   \ftext{Observation} & O &::=& \cdot \mid c; O\\
  %% \end{array}
  %% \]
